---
title: "Tree_plotting"
author: "Nations"
date: "2/11/2020"
output: html_document
---
THis is all updated from 20200220_tree_plot

Same as 20200220 but adding tribes in. This may get crazy!

DROP AETHOMYS_namaquensis!!

Revisiting the tree plot. What I need to do for the manuscript tree
X Change tip states to heat map, not points
X remove tip labels
X flip credible intervals at nodes
X Make node CIs into node dots, SO EASY!!
add fossil nodes
add phytools simmap nodes <- BUT I HAVE TO DROP TIPS FIRST! Maybe thats ok?? I'll try. 
X Check Sundamys states

I think I need two trees, one with simmap nodes for manuscript, one with node labels etc. for supplemental.


```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users/Dicrostonyx/Documents/Projects/AncSt/Manuscript/R/tree_plot/")
#knitr::opts_knit$set(root.dir = "/Users/esselstynlab/Documents/Jon//Users/esselstynlab/Documents/Jon/Murine_Ch_St/20190522_simmap/")
```

```{r}
library(tidyverse)
library(phytools)
library(ggtree)
library(geiger)
library(ggimage)
```


Tree and data load in
Data is already sorted and pruned to match tree
State #5 = NA
```{r}
tre <- read.beast(file = "435_MCC.tre")
tre2 <- read.newick(file = "435_MCC.nwk")
dat <- read.csv("state_435.csv", header=TRUE, row.names=1,stringsAsFactors=FALSE)
#pd <- readRDS(file = "simmap_50_summary.Rds")
#ace <- as.data.frame(pd$ace)
```
#keep only 1 state_name and rownames from dat
```{r}
dat2 <- dat[,2,FALSE]
```

```{r}
#dat$state_name <- factor(dat$state_name, levels = rev(levels(dat$state_name)))
```

Colors
```{r}
require(RColorBrewer)
cols <- c("#66a61e","#7570b3","#e6ab02", "#85D4E3", "#e5deda")
names(cols) = c("Arboreal", "General", "Terrestrial", "Amphibious", "Unknown")
```

#Trying to reverse nodes
SOMEHOW THERE IS AN "NA" in the a@data$height_0.95_HPD and I have NO IDEA WHY!
so I actually had to add another NA for some reason, then read it back in!
so now the data is xx.csv

original code form here :
https://groups.google.com/forum/#!msg/bioc-ggtree/wuAlY9phL9Q/L7efezPgDAAJ

Only Do this once! Once the xx.csv exists I don't need it anymore.
```{r}
#THIS SOMEHOW INTRODUCES A NA INTO THE matrix. I added another NA just below it and everything is gravy!
#xx <- matrix(unlist(tre@data$height_0.95_HPD))
#write.csv(xx, file ="xx.csv")
```

Manually add the NA, then read back in and manipulate
```{r}
xx <- read_csv(file ="xx.csv")
xx <- data.frame(V1=xx$V2[c(TRUE, FALSE)], V2=xx$V2[c(FALSE, TRUE)])
minmax = xx
```

This creates a dataframe with all nodes, including tips
```{r}
bar_df = data.frame(node_id=as.integer(tre@data$node),as.data.frame(minmax))
#changes column names
names(bar_df) = c('node_id','min','max')
#This removes tips
bar_df = bar_df %>% filter(node_id > Ntip(tre@phylo))
```

```{r}
b = ggtree(tre)
bar_df = bar_df %>% left_join(b$data, by=c('node_id'='node')) %>% select(node_id,min,max,y)
```
Now bar_DF is my baby!

#### Circular Version MODIFIED
Main tree with clase labels
```{r}
tre3 <- ggtree(tre) + theme_tree2() 
tre2 <- revts(tre3)
tre3 <- ggtree(tre, layout = "fan", open.angle=7) #+ theme_tree2() 
tre2 <- revts(tre3) 

tre1 <- tre2 + scale_x_continuous(breaks=c(-21:0), labels=c("", 20,"","","","",15,"","","","",10,"","","","",5,"","","","",""), limits = c(-21, 9)) + 
  # trying to make node points instead of nodelabs
        #geom_nodelab(aes(x=branch, label=round(posterior, 2), subset = !is.na(as.numeric(posterior)) & as.numeric(posterior) < 0.94), vjust=-.6, hjust = .8, size = 1)   + 
          geom_nodepoint(aes( label=posterior, subset = !is.na(as.numeric(posterior)) & as.numeric(posterior) > 0.9), size = 1.7, color ="grey30", alpha = 0.8)   +
  #this was for the old way of adding 
        #geom_range(range='height_0.95_HPD', color='#C93312', alpha=.3, size=1, branch.length="height") +
  #This adds the new bars in!!
  geom_segment(aes(x=-min, y=y+0, xend=-max, yend=y+0), data=bar_df, color='royalblue2', alpha = 0.7) +
  #These are tribe labels
  geom_cladelabel(node=625,  label = "Apodemini", align = T, offset = 4.5,  offset.text = 0.5, barsize = 2.2, color = c("grey80", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=558,   label = "Arvicanthini", align = T, offset = 4.5,  offset.text = 2.3, barsize = 2.2,  color = c("grey80", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=440,   label = "Hydromyini", align = T, offset = 4.5,  offset.text = 0.5, barsize = 2.2,  color = c("grey80", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=650,   label = "Malacomyini", align = T, offset = 4.5,  offset.text = 0.5, barsize = 2.2,  color = c("grey40", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=620,   label = "Millardini", align = T, offset = 4.5,  offset.text = 3.7, barsize = 2.2,  color = c("grey80", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=652,   label = "Murini", align = T, offset = 4.5,  offset.text = 0.5, barsize = 2.2,  color = c("grey80", "black"), fontface = "bold", fontsize = 5) +  
geom_cladelabel(node=606,   label = "Otomyini", align = T, offset = 4.5,  offset.text = 2.9, barsize = 2.2,  color = c("grey40", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=856,   label = "Phloeomyini", align = T, offset = 4.5,  offset.text = 0.5, barsize = 2.2,  color = c("grey40", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=683,   label = "Praomyini", align = T, offset = 4.5,  offset.text = 0.7, barsize = 2.2,  color = c("grey40", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=729,   label = "Rattini", align = T, offset = 4.5,  offset.text = 3, barsize = 2.2,  color = c("grey40", "black"), fontface = "bold", fontsize = 5) +

#Divisions
# Divisions with the same names as tribes? Well just add them in to start
geom_cladelabel(node=856,   label = "Phloeomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8, color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=551,   label = "Chiropodomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +
geom_cladelabel(node=519,   label = "Chrotomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=512,   label = "Pogonomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +
geom_cladelabel(node=445,   label = "Mallomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=454,   label = "Hydromys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +  
geom_cladelabel(node=465,   label = "Conilurus", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=468,   label = "Uromys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +
geom_cladelabel(node=480,   label = "Pseudomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=841,   label = "Maxomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +
geom_cladelabel(node=832,   label = "Echiothrix", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8, color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=801,   label = "Dacnomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +
geom_cladelabel(node=799,   label = "Berylmys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=776,   label = "Bunomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +
geom_cladelabel(node=736,   label = "Rattus", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=620,   label = "Millardia", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +  
geom_cladelabel(node=606,   label = "Otomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=605,   label = "Golunda", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +
geom_cladelabel(node=597,   label = "Hybomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=563,   label = "Aethomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +
geom_cladelabel(node=568,   label = "Grammomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8, color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=596,   label = "Dasymys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +
geom_cladelabel(node=578,   label = "Arvicanthis", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=683,   label = "Stenocephlemys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +
geom_cladelabel(node=625,   label = "Apodemus", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey80", "black"), fontsize = 2.9) +
geom_cladelabel(node=650,   label = "Malacomys", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey40", "black"), fontsize = 2.9) +  
geom_cladelabel(node=652,   label = "Mus", align = T, offset = 2.5,  offset.text = 0.5, barsize = 4.8,  color = c("grey80", "black"), fontsize = 2.9) 
```
heatmap for tips
```{r}
  pp1 <- gheatmap(tre1, dat[, 3, F], offset=0.01,
                  width=.07,
                  #colnames=F,
                  colnames_offset_y = 1000,
                  colnames_offset_x = 1000) 

  pp1 <- pp1 + scale_fill_manual(values = cols) + 
    theme(legend.position = c(0.1, 0.7)) +
    theme(legend.title = element_blank()) +
    #guides(colour = guide_legend(title.position = "right")) +
  guides(colour = guide_legend(override.aes = list(size=8))) +
  labs(color="Locomotor State") 

```
Adding in the time scale
```{r}
pp2 <- pp1 + geom_treescale(x=-17, y = 441, width=1, color='grey80', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-16, y = 441, width=1, color='black', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-15, y = 441, width=1, color='grey80', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-14, y = 441, width=1, color='black', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-13, y = 441, width=1, color='grey80', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-12, y = 441, width=1, color='black', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-11, y = 441, width=1, color='grey80', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-10, y = 441, width=1, color='black', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-9, y = 441, width=1, color='grey80', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-8, y = 441, width=1, color='black', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-7, y = 441, width=1, color='grey80', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-6, y = 441, width=1, color='black', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-5, y = 441, width=1, color='grey80', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-4, y = 441, width=1, color='black', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-3, y = 441, width=1, color='grey80', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-2, y = 441, width=1, color='black', offset = -5, linesize = 2, fontsize = 0) +
geom_treescale(x=-1, y = 441, width=1, color='grey80', offset = -5, linesize = 2, fontsize = 0)

```

fossils
```{r}
pp3 <- pp2 +
  geom_point2(aes(subset=(node==437)), shape = 23, size=5, fill='black') +
  geom_point2(aes(subset=(node==553)), shape = 23, size=5, fill='black') +
  geom_point2(aes(subset=(node==557)), shape = 23, size=5, fill='black') +
  geom_point2(aes(subset=(node==563)), shape = 23, size=5, fill='black') +
  geom_point2(aes(subset=(node==580)), shape = 23, size=5, fill='black') +
  geom_point2(aes(subset=(node==625)), shape = 23, size=5, fill='black') +
  geom_point2(aes(subset=(node==652)), shape = 23, size=5, fill='black')

#pp3

output_file = "20200413_test.pdf"

ggsave(output_file, width = 15, height = 15)

```




## Divisions 
THis is how I got the nodes for the 
These are the same 
 X Apodemyini = Apodemus
 X Hapalomyini =  Hapalomys = ROOT
 X Malacomyini = Malacomys
 X Milardini = Millardia
 X Murini = Mus
 X Otomyini = Otomys
 X Phloeomyini = Phloeomys
 
 Colomys is nested in Stenocephalemys 
 

```{r}
anctre <- read.newick(file = "435_MCC.nwk")
```
 
 
 Phloeomys is 832
```{r Phloeomys 856}
getMRCA(anctre, tip = c("Phloeomys_cumingi", "Crateromys_heaneyi"))
```

```{r Chiropodomys 551}
getMRCA(anctre, tip = c("Chiropodomys_gliroides", "Chiropodomys_major"))
```


```{r Chrotomys 519}
getMRCA(anctre, tip = c("Archboldomys_maximus", "Apomys_datae"))
```


```{r Pogonomys 512}
getMRCA(anctre, tip = c("Pogonomys_sylvestris", "Hyomys_goliath"))
```


```{r Mallomys 445}
getMRCA(anctre, tip = c("Coccymys_ruemmleri", "Mallomys_aroensis"))
```


```{r Hydromys 454}
getMRCA(anctre, tip = c("Crossomys_moncktoni", "Xeromys_myoides"))
```


```{r Conilurus 465}
getMRCA(anctre, tip = c("Leporillus_conditor", "Mesembriomys_macrourus"))
```


```{r Uromys 468}
getMRCA(anctre, tip = c("Uromys_caudimaculatus", "Melomys_leucogaster"))
```


```{r Pseudomys 480}
getMRCA(anctre, tip = c("Pseudomys_bolami", "Leggadina_forresti"))
```


```{r Maxomys 841}
getMRCA(anctre, tip = c("Maxomys_moi", "Maxomys_whiteheadi"))
```


```{r Echiothrix 832}
getMRCA(anctre, tip = c("Sommeromys_macrorhinos", "Tateomys_macrocercus"))
```


```{r Dacnomys 801}
getMRCA(anctre, tip = c("Saxatilomys_paulinae", "Niviventer_eha"))
```


```{r Berylmys 799}
getMRCA(anctre, tip = c("Berylmys_manipulus", "Berylmys_bowersi"))
```


```{r Bunomys 776}
getMRCA(anctre, tip = c("Bunomys_torajae", "Rattus_timorensis"))
```


```{r Rattus 736}
getMRCA(anctre, tip = c("Diplothrix_legata", "Rattus_steini"))
```


```{r Millardia 620}
getMRCA(anctre, tip = c("Millardia_meltada", "Cremnomys_cutchicus"))
```
 
```{r Otomys 606}
getMRCA(anctre, tip = c("Otomys_tropicalis", "Otomys_irroratus"))
``` 


```{r Golunda 605}
getMRCA(anctre, tip = c("Oenomys_hypoxanthus", "Golunda_ellioti"))
```


```{r Hybomys 597}
getMRCA(anctre, tip = c("Hybomys_planifrons", "Hybomys_badius"))
```

```{r Aethomys 563}
getMRCA(anctre, tip = c("Aethomys_hindei", "Aethomys_nyikae"))
```


```{r Grammomys 568}
getMRCA(anctre, tip = c("Grammomys_dolichurus", "Thallomys_loringi"))
```


```{r Dasymys 596}
getMRCA(anctre, tip = c("Dasymys_incomtus", "Dasymys_rufulus"))
```


```{r Arvicanthis 578}
getMRCA(anctre, tip = c("Lemniscomys_bellieri", "Desmomys_harringtoni"))
```


```{r Stenocephalemys 683}
getMRCA(anctre, tip = c("Mastomys_natalensis", "Mastomys_pernanus"))
```


```{r Apodemus 625}
getMRCA(anctre, tip = c("Apodemus_hermonensis", "Tokudaia_osimensis"))
```
 

```{r Malacomys 650}
getMRCA(anctre, tip = c("Malacomys_longipes", "Malacomys_edwardsi"))
```


```{r Mus 652}
getMRCA(anctre, tip = c("Mus_caroli", "Mus_indutus"))
```



