---
title: "Untitled"
author: "Jon Nations"
date: "4/28/2020"
output: html_document
---
```{r setup, include=FALSE}
knitr::opts_knit$set(root.dir = "/Users/Dicrostonyx/Documents/Projects/AncSt/Manuscript/R/tree_plot/")
#knitr::opts_knit$set(root.dir = "/Users/esselstynlab/Documents/Jon//Users/esselstynlab/Documents/Jon/Murine_Ch_St/20190522_simmap/")
```

```{r}
library(tidyverse)
library(phytools)
library(ggtree)
library(geiger)
library(wesanderson)
library(ggimage)
```


Tree and data load in
Data is already sorted and pruned to match tree
State #5 = NA
```{r}
tre <- read.beast(file = "435_MCC.tre")
tre2 <- read.newick(file = "435_MCC.nwk")
dat <- read.csv("state_434_DROPTIP.csv", header=TRUE, row.names=1,stringsAsFactors=FALSE)
#pd <- readRDS(file = "simmap_50_summary.Rds")
#ace <- as.data.frame(pd$ace)
```
#keep only 1 state_name and rownames from dat
```{r}
dat2 <- dat[,2,FALSE]
```

```{r}
getMRCA(tre2, c("Micaelamys_namaquensis", "Aethomys_namaquensis"))
```


```{r}
#dat$state_name <- factor(dat$state_name, levels = rev(levels(dat$state_name)))
```

Colors
```{r}
require(RColorBrewer)
cols <- c("#66a61e","#7570b3","#e6ab02", "#85D4E3", "#e5deda")
names(cols) = c("Arboreal", "General", "Terrestrial", "Amphibious", "Unknown")
```

#Trying to reverse nodes
SOMEHOW THERE IS AN "NA" in the a@data$height_0.95_HPD and I have NO IDEA WHY!
so I actually had to add another NA for some reason, then read it back in!
so now the data is xx.csv

original code form here :
https://groups.google.com/forum/#!msg/bioc-ggtree/wuAlY9phL9Q/L7efezPgDAAJ

THis only needs to be done once! That's why it's blocked out.
```{r}
#THIS SOMEHOW INTRODUCES A NA INTO THE matrix. I added another NA just below it and everything is gravy!
#xx <- matrix(unlist(tre@data$height_0.95_HPD))
#write.csv(xx, file ="xx.csv")
```

Manually add the NA, then read back in and manipulate
```{r}
xx <- read_csv(file ="xx.csv")
xx <- data.frame(V1=xx$V2[c(TRUE, FALSE)], V2=xx$V2[c(FALSE, TRUE)])
minmax = xx
```

This creates a dataframe with all nodes, including tips
```{r}
bar_df = data.frame(node_id=as.integer(tre@data$node),as.data.frame(minmax))
#changes column names
names(bar_df) = c('node_id','min','max')
#This removes tips
bar_df = bar_df %>% filter(node_id > Ntip(tre@phylo))
```

```{r}
b = ggtree(tre)
bar_df = bar_df %>% left_join(b$data, by=c('node_id'='node')) %>% select(node_id,min,max,y)
```
Now bar_DF is my baby!

#### Circular Version MODIFIED
Main tree with clase labels
```{r}
tre3 <- ggtree(tre) + theme_tree2() 
tre2 <- revts(tre3)
tre3 <- ggtree(tre, layout = "fan", open.angle=7) #+ theme_tree2() 
tre2 <- revts(tre3) 

tre1 <- tre2 + scale_x_continuous(breaks=c(-21:0), labels=c("", 20,"","","","",15,"","","","",10,"","","","",5,"","","","",""), limits = c(-21, 9)) + 
  # trying to make node points instead of nodelabs
        #geom_nodelab(aes(x=branch, label=round(posterior, 2), subset = !is.na(as.numeric(posterior)) & as.numeric(posterior) < 0.94), vjust=-.6, hjust = .8, size = 1)   + 
          geom_nodepoint(aes( label=posterior, subset = !is.na(as.numeric(posterior)) & as.numeric(posterior) > 0.9), size = 1.7, color ="grey30", alpha = 0.8)   +
  #this was for the old way of adding 
        #geom_range(range='height_0.95_HPD', color='#C93312', alpha=.3, size=1, branch.length="height") +
  #This adds the new bars in!!
  geom_segment(aes(x=-min, y=y+0, xend=-max, yend=y+0), data=bar_df, color='royalblue2', alpha = 0.7) +
  #These are tribe labels
  geom_cladelabel(node=625,  label = "Apodemini", align = T, offset = 4.5,  offset.text = 0.5, barsize = 2.2, color = c("grey80", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=558,   label = "Arvicanthini", align = T, offset = 4.5,  offset.text = 2.3, barsize = 2.2,  color = c("grey80", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=440,   label = "Hydromyini", align = T, offset = 4.5,  offset.text = 0.5, barsize = 2.2,  color = c("grey80", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=650,   label = "Malacomyini", align = T, offset = 4.5,  offset.text = 0.5, barsize = 2.2,  color = c("grey40", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=620,   label = "Millardini", align = T, offset = 4.5,  offset.text = 3.7, barsize = 2.2,  color = c("grey80", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=652,   label = "Murini", align = T, offset = 4.5,  offset.text = 0.5, barsize = 2.2,  color = c("grey80", "black"), fontface = "bold", fontsize = 5) +  
geom_cladelabel(node=606,   label = "Otomyini", align = T, offset = 4.5,  offset.text = 2.9, barsize = 2.2,  color = c("grey40", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=856,   label = "Phloeomyini", align = T, offset = 4.5,  offset.text = 0.5, barsize = 2.2,  color = c("grey40", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=683,   label = "Praomyini", align = T, offset = 4.5,  offset.text = 0.7, barsize = 2.2,  color = c("grey40", "black"), fontface = "bold", fontsize = 5) +
geom_cladelabel(node=729,   label = "Rattini", align = T, offset = 4.5,  offset.text = 3, barsize = 2.2,  color = c("grey40", "black"), fontface = "bold", fontsize = 5) 
```

```{r}
pp1 <- tre1 %<+% dat + geom_tippoint(aes(color=state_name), size = 2.2) +
  scale_color_manual(values = cols) + 
    theme(legend.position = c(0.1, 0.7)) +
  guides(colour = guide_legend(override.aes = list(size=8))) +

  labs(color="Locomotor State") 

pp2 <- pp1 +  geom_tiplab2(size=1.4, offset=0.31, align=TRUE, aes(angle=angle))

pp2 


output_file = "20200428_Supp_Tree.pdf"

ggsave(output_file, width = 15, height = 15)


```

